Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-08 main_paper.tex
Delete CI formula in the simulation section
This commite deletes CI fomula in the simulation section because I just
noticed that it is clearly explained in Algorithm 2.

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals.\footnote{The bootstrap principle ensures that $\hat\tau^{\prime*}(h,b) - \big[\hat g_+(0) - \hat g_-(0)\big]$ approximates the distribution of $\hat\tau^{\prime}(h,b) - \tau$, so the confidence interval of level 0.95 is constructed as$(\hat\tau^{\prime}(h,b) + \big[\hat g_+(0) - \hat g_-(0)\big] - \hat\tau^{\prime*}(h,b)_{0.975}, \hat\tau^{\prime}(h,b) + \big[\hat g_+(0) - \hat g_-(0)\big] - \hat\tau^{\prime*}(h,b)_{0.025})$, where $\hat\tau^{\prime*}(h,b)_{0.975}$ and $\hat\tau^{\prime*}(h,b)_{0.025}$ are the 97.5 and 2.5 percentiles of bootstrap distribution of bias-corrected estimator.} We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT. We also estimate CCT's bias corrected procedure with AMSE-optimal bandwidths and
the uniform kernel for direct comparison.

>>>>

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT. We also estimate CCT's bias corrected procedure with AMSE-optimal bandwidths and
the uniform kernel for direct comparison.
